Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-09 tikz_images/proof.tex
Finished problem decomposition section - updated the start of the crypto section to suit the now moved decomposition discussion Updated the section summary to correctly summarise the new sections Added the notation paragraph Updated all Tikz images to be narrower as it looks nicer - also updated all the tikzimage .tex's to include preamble code so they look the same when opened in TikzEdt

\begin{tikzpicture}[font=\footnotesize]
% Bounding box
\draw [gray] (0,-0.25) rectangle (8,7.5);

% Outer adversary rectangle
\draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
% Inner adversary rectangle
\draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);

% Adversaries and challenger
\node at (4,3.5) {\LARGE$\mathcal{A}'$};
\node at (4,6) {\LARGE$\mathcal{A}$};
\node at (4,0.5) {\LARGE$\mathcal{C}$};

@@

\node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
\draw [-latex] (2,4.5) --(2,5.5);

\node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
\draw [-latex] (6,5.5) -- (6,4.5);

\node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
\draw [-latex] (6,2.75) -- (6,1.75);

\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\small]
    % Bounding box
    \draw [gray] (0,0) rectangle (6.5,6.5);

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};

@@

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
\end{tikzpicture}
